The \dealii Library, Version 9.5

### 2023-06-23 9.5/paper.tex
One more code gallery program.

There are also three new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item \textit{``A posteriori error estimator for first order hyperbolic problems''},
  contributed by Marco Feder;
  \item \textit{``Distributed moving laser heating''}, contributed by
  Hongfeng Ma and Tatiana E.~Itina;
  \item \textit{``Generalized Swift-Hohenberg Equation Solver''}, contributed by
  Sam Scheuerman.
\end{itemize}

>>>>

There are four new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item \textit{``A posteriori error estimator for first order hyperbolic problems''},
  contributed by Marco Feder;
  \item \textit{``Distributed moving laser heating''}, contributed by
  Hongfeng Ma and Tatiana E.~Itina;
  \item \textit{``Generalized Swift-Hohenberg Equation Solver''}, contributed by
    Sam Scheuerman.
  \item \textit{``Information density-based mesh refinement''},
    contributed by Wolfgang Bangerth.
\end{itemize}
